### 2017-07-14 pkg/model4you/inst/JORS/man_model4you.Rnw
start vignette and delete GBSG2 from manuscript
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1506 255f4249-2263-4417-b1ea-8498779e27a7

<<setup, echo=FALSE>>=
library("knitr")
knitr::opts_chunk$set(cache = TRUE, message = FALSE, fig.align = "center")

@@

<<math_tree, fig.width = 13, fig.cap = "Personalised model tree for GBSG2 data.">>=  
## compute tree
(tr_math <- pmtree(bmod_math, control = ctree_control(maxdepth = 2)))
plot(tr_math, terminal_panel = node_pmterminal(tr_math, 
                                               plotfun = lmplot, 
                                               confint = TRUE))
@

@@

% \paragraph{Analysis of the German Breast Cancer Study Group 2}
% 
% <<GBSG2_prep>>=
% library("survival")
% data("GBSG2", package = "TH.data")
% @
% 
% <<GBSG2_bmod, fig.height = 5, out.width = '0.7\\textwidth', fig.cap = "Base model for GBSG2 data.">>=
% bmod <- survreg(Surv(time, cens) ~ horTh, data = GBSG2, model = TRUE)
% survplot(bmod)
% 
% ## extract coefficients and confidence intervals
% coefs <- coef(bmod)
% ci <- confint(bmod)
% coefs <- cbind(coefs, ci)
% 
% ## prepare for plotting
% digits <- 2
% cf <- format(round(coefs, digits), nsmall = digits)
% colnams <- colnames(cf)
% colnams[1] <- "theta"
% gridExtra::grid.table(
%   cf, cols = colnams,
%   theme = ttheme_minimal(colhead = list(fg_params = list(parse = TRUE))),
%   vp = viewport(x = 0, y = 0, width = 0.7, height = 0.4,
%                 just = c("left", "bottom"))
% )
% @
% 
% <<GBSG2_tree, fig.width = 9, fig.cap = "Personalised model tree for GBSG2 data.">>=
% tr <- pmtree(bmod)
% plot(tr, terminal_panel = node_pmterminal(tr, plotfun = survplot, 
%                                           confint = TRUE))
% @
% 
% <<GBSG2_forest>>=
% frst <- pmforest(bmod)
% @
% 
% <<GBSG_pmod1>>=
% newpatient_i <- data.frame(age = 60, menostat = "Post", tsize = 20, tgrade = "II",
%                            pnodes = 3, progrec = 50, estrec = 60)
% mod_i <- pmodel(x = frst, fun = identity, newdata = newpatient_i)
% @
% 
% <<GBSG2_pmod>>=
% coeffun <- function(model) {
%   ## model coefficients
%   coefs <- c(coef(model), scale = model$scale)
%   
%   ## difference in median survival 
%   p = 0.5
%   coefs["median_s0"] <- qweibull(p = p, shape = 1/coefs["scale"], 
%                                  scale = exp(coefs["(Intercept)"]))
%   coefs["median_s1"] <- qweibull(p = p, shape = 1/coefs["scale"], 
%                                  scale = exp(coefs["(Intercept)"] + coefs[2]))
%   coefs["median_sdiff"] <- coefs["median_s1"] - coefs["median_s0"]
%   
%   return(coefs)
% }
% coefs <- pmodel(x = frst, fun = coeffun, OOB = TRUE)
% 
% ## add to data and plot
% dpdat <- cbind(coefs, GBSG2)
% znam <- names(GBSG2)[!(names(GBSG2) %in% c("horTh", "time", "cens"))]
% 
% dplot <- function(z) {
%   p <- ggplot(dpdat, aes_string(x = z, y = "median_sdiff")) 
%   if(is.factor(dpdat[, z])) {
%     p + geom_boxplot()
%   } else {
%     p + geom_point(alpha = 0.2) + 
%       geom_smooth(fill = NA, method = "loess")
%   }
% }
% dps <- lapply(znam, dplot)
% do.call(grid.arrange, dps)
% 
% do.call(grid.arrange, lapply(dps, function(p) {
%   dmin <- min(dpdat$median_sdiff)
%   dq <- quantile(dpdat$median_sdiff, 0.99)
%   p + coord_cartesian(ylim = c(dmin, dq))
% }))
% @

>>>>

<<setup, echo=FALSE>>=
library("knitr")
knitr::opts_chunk$set(cache = FALSE, message = FALSE, fig.align = "center")

@@

<<math_tree, fig.width = 13, fig.cap = "Personalised model tree for math exam.">>=  
## compute tree
(tr_math <- pmtree(bmod_math, control = ctree_control(maxdepth = 2)))
plot(tr_math, terminal_panel = node_pmterminal(tr_math, 
                                               plotfun = lmplot, 
                                               confint = TRUE))
@

@@
